HyperLogLog: Exponentially Bad in Adversarial Settings

### 2020-10-12 docs/HLL_exp_bad/main.tex
typo

The interpretation of the above theorem is that if $F$ is a good PRF, then $\mbox{Adv}^{\tiny\mbox{PRF}}_{F}({\cal B})$ should be small for any adversary ${\cal B}$ running in a reasonable amount of time. Hence we can conclude that the advantage of any S4 adversary against HLL using PRF $F$ is also small.

>>>>

The interpretation of the above theorem is that if $F$ is a good PRF, then $\mbox{Adv}^{\mbox{\tiny PRF}}_{F}({\cal B})$ should be small for any adversary ${\cal B}$ running in a reasonable amount of time. Hence we can conclude that the advantage of any S4 adversary against HLL using PRF $F$ is also small.
